Simultaneous Elicitation of Scoring Rule and Agents Preferences for Robust Winner Determination

### 2020-01-21 draft.tex

The \strat{Pessimistic} strategy selects the question that leads to minimal regret in the worst case, considering both possible answers to the question. Assume that a question leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile_2, W_2)$, depending on the answer. Then the badness of the question in the worst case is:
\[\max_{i=1,2} \MMR(\pprofile_i,W_i) \]
This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes the measure. Note that other aggregators than $\max$ can be used as well. %We use the $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
It uses the $\leximax$ criterion as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest of this value.
 We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$. For small dimensions, it gives us an estimate of an upper bound to the possible quality of a strategy.

The \strat{Pessimistic with heuristic} strategy is a much faster version of the previous strategy. It chooses among the set of possible questions in the same way, but considers only one possible question per voter and one possible question about the weights, thereby reducing the complexity to $O(n^2 m^3)$. \commentOC{Is this right? If we can solve easily a size $(m, n) = (15, 15)$ with the Pwh strategy, which requires about $15^5 \approx 8 . 10^5$ operations, we should be able to solve easily a size $(m, n) = (6, 6)$ with the Pessimistic strategy, which requires about $6^7 \approx 3 . 10^5$ operations.}
The possible question associated to each voter is determined using a heuristic proposed by \citet{Boutilier2006}. \commentOC{Please check that the reference is correct and explain briefly their heuristic.} The possible question to the committee is determined as follows. \commentOC{I am not so happy about this. If we have time, we should consider one question per rank and drop the tau business.}
Recall that $x^{*}$ is the minimax regret optimal alternative, and $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$, $\bar{\profile}$ and $\bar{\w}$ are the adversarial choices, thus, the instantiations that, given the choice of $x^*$, maximize the regret. 
Define $w^\tau = \argmin_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$.
The vector $\bar{w} - w^\tau = \argmax_{\w \in W} (s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)) - \argmin_{\w \in W} (s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w))$ estimates our uncertainty about the weights $\w$ when fixing our choice of alternative $x^*$ and the adversarial choices $\bar{y}$ and $\bar{\profile}$.
Therefore, we compare component-wise $\bar{\w}$ and $\w^{\tau}$, to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.

>>>>

The \strat{Pessimistic} strategy selects the question that leads to minimal regret in the worst case, considering both possible answers to the question. Assume that a question leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile_2, W_2)$, depending on the answer. Then the badness of the question in the worst case is:
\[\max_{i=1,2} \MMR(\pprofile_i,W_i) \]
This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes the measure. Note that other aggregators than $\max$ can be used as well. %We use the $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
However, to avoid the absorption property of max, we adopt the $\leximax$ criterion as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest of this value.
 We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$. For small dimensions, it gives us an estimate of an upper bound to the possible quality of a strategy.

%TODO Limited; chair
The \strat{LimitedPessimistic} strategy uses the same criterion as the pessimistic strategy, but only considering a small set of candidate questions.
For each voter, a candidate question is chosen by considering the heuristic proposed by \citet{Lu2011}. 
For the chair, we define
\begin{align}
w^\tau & = \argmin_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w), \label{eq:tau} 
\end{align}
and compare component-wise $\bar{\w}$ and $\w^{\tau}$, to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
\commentOC{I am not so happy about this. If we have time, we should consider one question per rank and drop the tau business.}
We then evaluate, for each candidate question, the minimax regret for each possible answer; finally we choose the best according to $\leximax$.
%\commentOC{Reducing the complexity to $O(n^2 m^3). Is this right? If we can solve easily a size $(m, n) = (15, 15)$ with the Pwh strategy, which requires about $15^5 \approx 8 . 10^5$ operations, we should be able to solve easily a size $(m, n) = (6, 6)$ with the Pessimistic strategy, which requires about $6^7 \approx 3 . 10^5$ operations.}
